\documentclass[11pt]{article}

% -------------------------------------------------------------------------------------------------
% Packages 
\usepackage{calc}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{xhfill}

% Layout: Puts the section titles on left side of page
\reversemarginpar

\usepackage[paper=a4paper,
            includefoot, 			% Uncomment to put page number above margin
            marginparwidth=30.5mm,	% Length of section titles
            marginparsep=1.5mm,		% Space between titles and text
            margin=25mm,			% 25mm margins
            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{customaqua}{rgb}{0.192,0.518,0.608}
\definecolor{customlightaqua}{rgb}{0.576,0.804,0.867}
\hypersetup{colorlinks,breaklinks,
            linkcolor=customaqua,urlcolor=customaqua,
            anchorcolor=customaqua,citecolor=customaqua}


% -------------------------------------------------------------------------------------------------
% Macros
\newcommand{\makeheading}[3]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
								\centering
                {\huge \sffamily \color{gray}{#1}}{\huge \sffamily #2}\hspace{0.2cm}\rule[-7pt]{1.5pt}{27pt}\hspace{0.2cm}{\color{customaqua}\huge \bfseries #3}\\[-0.15\baselineskip]%
                 \rule[-1pt]{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape \bfseries #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section 
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}


% -------------------------------------------------------------------------------------------------
% Main document

\begin{document}
\makeheading{Storm}{Collins}{Curriculum Vitae}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table 
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2.3in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-20pt}p{\rcollength}}
	collins.storm@gmail.com\\
 	+27 66 273 3039
\end{tabular}

\hspace{0pt}\xrfill[-8pt]{0.5pt}[customaqua]\hspace{0pt}


% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Work Experience}
\textbf{Consulting \& Audit}
\blankline
\begin{outerlist}
					\item[] \textbf{\textcolor{customaqua}{Deloitte}}, Financial Services Advisory, Valuations, Senior Manager (May 2019 - Present)
					\begin{innerlist}
						\item BAU management of junior staff members, managing client relationships with regards to delivery, reporting \& explaining results, strategy for the team, proposals for new business, 
						\item Derivative pricing in both IFRS 2 \& IFRS 13 standards, wide spectrum of instruments from employee share schemes, BEE options, to CVA, DVA, FVA, \& KVA,
						\item Instrumental in spearheading a revamp of their existing limited C\# library for derivative pricing as well as educating junior members,
					\end{innerlist}

\end{outerlist}
%
\blankline


\textbf{Investment Banking}
%
\blankline
\begin{outerlist}
	\item[] \textbf{\textcolor{customaqua}{Standard Bank CIB}}, Trading Risk Analytics, (April 2014 - May 2019)
					\begin{innerlist}
						\item Developed a framework, in C\#, for performing stress testing analysis of counterparty credit risk which integrated with Adaptiv to calculate relevant metrics such as PFE, EPE, \& Economic Capital for various stressed economic scenarios.
						\item Fielded wrong way risk queries from credit managers with regards to the exposure generated by the conditional default model.
						\item Involved with vetting the consistency of exposures \& methodology in numerous trading system migrations \& Adaptiv upgrades.
						\item Performed relevant analysis for how to best accommodate exotic type instruments that can't be accurately captured in Adaptiv.
						\item Performed bespoke PFE calculations for instruments not catered for by Adaptiv.
						\item Fielded queries from model validation with regards to reviews of stochastic processes used in Monte Carlo simulations.
						\item Helped with the analysis \& implementation of back testing stochastic process parameters \& models via a framework developed in Python \& C\#.
						\item Assisted with upgrading C\# code for calibrating stochastic process parameters. 
						\item Fielded queries about collateral algorithm.
						\item Assisted Asset Control in implementing revised market data specifications required for Adaptiv exposure calculations.
					\end{innerlist}
					\item[] Independent Valuations and Model Controller at ABSA Capital (February 2012 - March 2014)
					\begin{innerlist}
						\item Price and bid offer testing of Equity Derivative and Prime Services desks using observable/liquid market data.
						\item Performed FVA, CVA, and CCRA calculations attributing moves in counterparty credit and funding exposure. 
						\item Reviewed new product approvals and structured trade reviews in equities, prime services and credit. 
						\item Performed observability analysis of market data.
						\item Investigated valuation issues resulting from the application of OIS discounting, CVA, DVA and FVA to derivatives pricing. 
						\item Investigated \& kept up to speed with relevant pricing methodologies for equity derivatives.
					\end{innerlist}
					\item[] Junior Quantitative Analyst at ABSA Capital (February 2010 - January 2012) 
						\begin{innerlist}
							\item Implemented/researched various pricing and hedging  methodologies for various asset classes (mainly credit and fixed income).
							\item Aided in implementation of multi-curve system for FVA calculations.
							\item Aided in development of standard Excel pricing platform via C\# and C++.
							\item Performed various statistical analyses of market data for trading desks.
						\end{innerlist}
\end{outerlist}

\hspace{0pt}\xrfill[0pt]{0.5pt}[customaqua]\hspace{0pt}
\blankline


% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Tertiary Education}
{\textbf{Georgia Institute of Technology}}, Atlanta, Georgia
\begin{outerlist}
	\item[] Masters of Science in Computer Science, \emph{In Progress},
	\begin{innerlist}
     	\item I was accepted into a part-time masters degree in computer science at a highly respected 
     		 American university in 2019, which I intend to complete by 2022, 
        	\item The masters degree is entirely by coursework \& I've elected to take the 
        		 \emph{computing systems} stream which is primarily focused on software development, 
        		 operating systems, high performance computing etc.\ \& to complement it with courses from 
        		 the machine learning stream,
     \end{innerlist}
\end{outerlist}


% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
{\textbf{University of the Witwatersrand}}, Johannesburg
\begin{outerlist}
	\item[] Masters of Science, {Physics}, 2008, \emph{with distinction}
		\begin{innerlist}
        		\item Dissertation Topic: \textit{\href{http://wiredspace.wits.ac.za/bitstream/handle/10539/7200/MSc\_Dissertation\_of\_StormCollins\%280408399D\%29\_2008.pdf?sequence=1}{Multi-Trace Operators and the Gauge-Gravity Correspondence}}
        		\item Supervisor: {Professor Robert S.~de~Mello~Koch}
        		\item Area of Study: String Theory (AdS/CFT Correspondence)
        	\end{innerlist}

	\item[] Bachelor of Science (Honours), {Advanced Mathematics of Finance}, 2009,
		   \emph{with distinction}
		\begin{innerlist}
			\item Honours Project, \textit{\href{http://www.wits.ac.za/files/rese4efda12f86a43e8a94975a9cd421b46.pdf}{A Low-Dimensional LIBOR Market Model}}
		\end{innerlist}
				
	\item[] Bachelor of Science (Honours), {Physics}, 2007, \emph{with distinction}
      	\begin{innerlist}
        		\item Honours Project, \textit{Quantum Statistics of Anyons}
        	\end{innerlist}
\end{outerlist}
\hspace{0pt}\xrfill[0pt]{0.5pt}[customaqua]\hspace{0pt}
\blankline


% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Publications}
\emph{Restricted Schur Polynomials and Finite N Counting.} Storm Collins, Physical Review \textbf{D 79}, 026002 (2009), \href{http://arxiv.org/pdf/0810.4217.pdf}{http://arxiv.org/pdf/0810.4217.pdf}

\blankline

\emph{Exact Multi-Matrix Correlators.} R.~Bhattacharyya, S.~Collins and 
			\\R.~de~Mello~Koch, Journal of High Energy Physics JHEP\textbf{03}(2008)044, 
			\\ \href{http://arxiv.org/pdf/0801.2061.pdf}{http://arxiv.org/pdf/0801.2061.pdf}
			
\hspace{0pt}\xrfill[0pt]{0.5pt}[customaqua]\hspace{0pt}
\blankline


% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{University Awards} 
	\begin{innerlist}
		\item Standard Bank Award for Honours in Advanced Mathematics of Finance (2009),
		\item CH Leon bursary (2009),
		\item South African Institute of Physics (SAIP) award for best Masters talk in theoretical physics (2008),
		\item Merck achievement award for best interdisciplinary third year BSc student (2006),
		\item Diamond research laboratory award for top third year physics student (2006),
		\item Frank Nabarro summer essay prize for Physics III (2006),
		\item Diamond research laboratory award for top second year physics student (2005),
	\end{innerlist}
\hspace{0pt}\xrfill[0pt]{0.5pt}[customaqua]\hspace{0pt}
\blankline


% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Computer Skills} 
\textbf{Programming Languages}
\blankline

	\begin{innerlist}
		\item \textbf{Advanced:} C\#, Matlab, Python (including Numpy \& Scipy). 
		\item \textbf{Intermediate:} C$\backslash$C++				
		\item \textbf{Basic:} Java, SQL
	\end{innerlist}

\blankline


% --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --  --
\textbf{Software Development}
\blankline

	\begin{innerlist}
		\item I've been involved with the scoping \& design of two significant quantitative software 	
			 projects, one at Deloitte \& one at Standard Bank CIB,
		\item Although not part of my original tertiary education I have supplemented my knowledge over 
			 the years in various pertinent areas including: Design patterns, continuous integration, 
			 version control, resource management, analysis \& verification, \& general software best 
			 practices, \& have become adept in several coding eco-systems.
	\end{innerlist}
\hspace{0pt}\xrfill[0pt]{0.5pt}[customaqua]\hspace{0pt}

\end{document}